Trail Saving on Backtrack

### 2020-02-18 paper.tex
results

\begin{figure}
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total Solved & SAT & UNSAT & Par-2 (x 10\textasciicircum{}6 s) \\ \hline
      cadical                  & 527          & 315 &  212  & 3.220                             \\ \hline
      cadical\_chrono          & 515          & 305 &  210  & 3.269                             \\ \hline
      cadical\_trail           & 520          & 307 &  213  & 3.248                             \\ \hline
      cadical\_trail\_enhanced & 524          & 315 &  209  & 3.216                             \\ \hline
    \end{tabular}
    \caption{Table of results for cadical or "chrono", version published in \cite{DBLP:conf/sat/MohleB19}.}
\end{figure}

\begin{figure}
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total Solved & SAT & UNSAT & Par-2 (x 10\textasciicircum{}6 s) \\ \hline
      cadical                  & 492          & 289 &  203  & 3.5020                            \\ \hline
      cadical\_chrono          & 498          & 292 &  206  & 3.4400                            \\ \hline
      cadical\_trail           & 493          & 290 &  203  & 3.5228                            \\ \hline
      cadical\_trail\_enhanced & 496          & 292 &  204  & 3.4847                            \\ \hline
    \end{tabular}
    \caption{Table of results for cadical, version pulled from github as of July 30, 2019.}
\end{figure}

>>>>

\begin{figure}
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total Solved & SAT & UNSAT & Par-2 (x 10\textasciicircum{}6 s) \\ \hline
      cadical                  & 532          & 314 &  218  & 3.220                             \\ \hline
      cadical\_chrono          & 525          & 308 &  217  & 3.269                             \\ \hline
      cadical\_trail           & 529          & 310 &  219  & 3.248                             \\ \hline
      cadical\_trail\_enhanced & 531          & 313 &  218  & 3.216                             \\ \hline
    \end{tabular}
    \caption{Table of results for cadical, version pulled from github as of January 1, 2020.}
\end{figure}

\begin{figure}
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total Solved & SAT & UNSAT & Par-2 (x 10\textasciicircum{}6 s) \\ \hline
      cadical                  & 492          & 289 &  203  & 3.5020                            \\ \hline
      cadical\_chrono          & 498          & 292 &  206  & 3.4400                            \\ \hline
      cadical\_trail           & 493          & 290 &  203  & 3.5228                            \\ \hline
      cadical\_trail\_enhanced & 496          & 292 &  204  & 3.4847                            \\ \hline
    \end{tabular}
    \caption{Table of results for cadical or "chrono", version published in \cite{DBLP:conf/sat/MohleB19}.}
\end{figure}
